### 2019-10-03 Sections/cryptowars.tex
CV attacks save

>>>>

\subsubsection{Attacks on the local oscillator}

In order to measure Alice's signal states, Bob needs to carry out quadrature measurements, which
are defined with respect to Alice's local oscillator. Since it is difficult to maintain coherence 
between Alice's and Bob's LO, often the Alice sends through the LO through the channel together with the signal states. This leaves open some side-channels which Eve can exploit. For example, she can reduce the error which the trusted parties would expect (e.g. of an intercept and resend attack), if she replaces the signal and LO with squeezed states. Other attacks of the LO include Eve exploiting the wavelength dependence of the beam splitters, shape of the LO pulse, phase noises and the non-linearity photo-detectors.

\subsubsection{Trojan horse attacks}
